---
title: "Journal (reproducible report)"
author: "Ubaid Ilyas"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.


# Chapter 2 Challenges

Last compiled: `r Sys.Date()`

This section will cover the challenges provided at the end of Chapter 2.
```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(lubridate)
library(readxl)
# 2.0 Importing Files ----
bikes_tbl <- read_excel("/Users/UBIL1/Desktop/TUHH/business/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("/Users/UBIL1/Desktop/TUHH/business/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("/Users/UBIL1/Desktop/TUHH/business/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 4.0 Joining Data ----
left_join(orderlines_tbl, bikes_tbl, by = c("product.id" = "bike.id"))%>%
  invisible()
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
# 5.0 Wrangling Data ----
bike_orderlines_joined_tbl %>% 
  select(category) %>%
  filter(str_detect(category, "^Mountain")) %>% 
  unique() %>%
  invisible()
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
```

## Bar Graph for Sales by location


```{r plot2.1, fig.width=12, fig.height=7}
#6.0 Chapter 2 Challenges ----

#6.1 Sales by State ----
sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  group_by(state) %>% 
  summarise(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))


sales_by_state_tbl%>%
  ggplot(aes(x = state, y = sales)) +
  geom_col(fill = "#2DC6D6") + 
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) +
 scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
 theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title    = "Revenue by State",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )

```


## Revenue by Year and Location
```{r plot2.2, fig.width=12, fig.height=7}

#6.0 Chapter 2 Challenges ----
#6.2 Sales by Year and State ----
sales_by_year_location_tbl<- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price, location) %>%
  mutate(year = year(order_date)) %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%  
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
sales_by_year_location_tbl %>%
  ggplot(aes(x = year, y = sales, fill = state)) +
  geom_col() + 
  geom_smooth(method = "lm", se = FALSE) +  
  facet_wrap(~ state) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and location",
    subtitle = "Each product category has an upward trend",
    fill = "State" # Changes the legend name
  )

```

# Chapter 3 Challenges
Last compiled: `r Sys.Date()`

This section will cover the challenges provided at the end of Chapter 3.

## Data via API
```{r tibble3.1}
#1.0 Load libraries ----
library(httr)
library(stringr)
library(tidyverse) 
library(rvest)     
library(jsonlite)  
library(scales)

#2.0 Getting Data via API
  resp<- GET("https://pokeapi.co/api/v2/ability/?limit=50&offset=20")
#3.0 Coversion to Tibble
    rawToChar(resp$content) %>%
    fromJSON() %>% 
    .[[4]] %>% 
    .[] %>% 
    as_tibble()%>%
    head(10)
```

## DB based on Model and Price
```{r tibble3.2}
#4.0 Read in the HTML for the Entire Webpage
html <- read_html("https://www.rosebikes.de/fahrr%C3%A4der/kinder")
#5.0 Web Scraping for Model Names
model_name <-  html %>% 
  html_nodes(css = ".catalog-product-tile__title") %>%
  html_text() %>%
  stringr::str_replace_all(pattern = "\n\n", replacement = " ") %>%
  stringr::str_extract("(?<=\\n).*(?=\\n)")
#6.0 Web Scraping for Prices
price <-  html %>% 
  html_nodes(css = ".product-tile-price__wrapper") %>%
  html_text()%>%
  stringr::str_extract(pattern = "[0-9]+") %>% 
  as.numeric() %>%
  dollar(big.mark = ".", 
         decimal.mark = ",", 
         prefix = "", 
         suffix = " €")
#7.0 Coversion to Tibble
tibble(model_name,price) %>% 
  head(10)
```


